{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-09-04 documents/acknowledgement.tex
Minted garbage
Quick ol' FDTD sim of lung

@@

This paper would have been absolutely impossible without the support of hundreds of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca. Thank you to all the dedicated authors that develop and maintain these tools.

@@

Dr. Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and

@@

Thanks to L.H. for wisdom regarding this project; P.B and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.

@@

The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models available at https://sites.utexas.edu/austinmanaustinwomanmodels/.

>>>>

%!TeX root = acknowledgement
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

Thanks to (Dr. ) Peter Barfuss for spending time reviewing drafts.

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca. Thank you to all the dedicated authors that develop and maintain these tools.

@@

Dr. Alex Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and

@@

Thanks to L.H. for wisdom regarding this project; and H.P. and i.9. for tolerating midnight ramblings and M.Q. for the hug.

@@

The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/.

### 2020-09-04 documents/safety.tex
Quick ol' FDTD sim of lung

Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations. \footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].} a loophole in the guidelines

>>>>

Because this is an ostensibly novel and niche mechanism, it may behoove us to briefly review the biological basis for the safety limits set by standards organizations. \footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].}
